Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-09-07 parts/massmodel.tex
typo fix

The mass will naturally depend on the lens and source redshifts, which
are unknown when a lens candidate is first identified.  However, this
is not a problem, because a model can be trivially rescaled to use
better redshift values, as they become available.  The mass
normalisation of the models is proportional, through the angular
critical density, to the factor $d_L\, d_S\, d_{LS}^{-1}$, where
$d_L,d_S$ and $d_{LS}$ are the usual angular-diameter distances.  In
the redshift ranges typical of galaxy lensing, the normalisation
factor is roughly proportional to the lens redshift, and weakly
dependent on the source redshift.  This work applies photometric
redshifts from the CFHTLS pipeline \citep{2009A&A...500..981C} to the
candidate lensing galaxies; the values range from $z=0.2$ to 1 (see
Table~\ref{tab:models}).  The source redshifts are assumed as $z=2$,
unless an unambiguous photometric redshift is available.  The lens
redshifts redshifts entail rather big uncertainties, up to a few tens
of percent.  The lensing masses are uncertain at the same level.  On
the other hand, the lensing masses in the sample range from
$10^{11}M_\odot$ to $10^{13}M_\odot$, hence the redshift uncertainty
is not so important in this preliminary analysis.
% \textcolor{red}{\bf IF: I would not say this is
% ``negligible'' but, rather, that the error in the redshift would lead to
%  surface mass density uncertainties of XX\%, which, for the
%  aim of the tentative analysis presented here, is an acceptable
%  result. You should also check and quantify properly the
%  uncertainty in the photo-z. What is the value claimed by the
%  CFHTLS group? I would say 5-10\% is a decent level, but you
%  are mentioning 10s of \% which is rather extreme!}.
% \textcolor{red}{\bf IF: Again, a simple quantification of the
% change you expect, for instance, if the source is at z=3 would be good.}

>>>>

The mass will naturally depend on the lens and source redshifts, which
are unknown when a lens candidate is first identified.  However, this
is not a problem, because a model can be trivially rescaled to use
better redshift values, as they become available.  The mass
normalisation of the models is proportional, through the angular
critical density, to the factor $d_L\, d_S\, d_{LS}^{-1}$, where
$d_L,d_S$ and $d_{LS}$ are the usual angular-diameter distances.  In
the redshift ranges typical of galaxy lensing, the normalisation
factor is roughly proportional to the lens redshift, and weakly
dependent on the source redshift.  This work applies photometric
redshifts from the CFHTLS pipeline \citep{2009A&A...500..981C} to the
candidate lensing galaxies; the values range from $z=0.2$ to 1 (see
Table~\ref{tab:models}).  The source redshifts are assumed as $z=2$,
unless an unambiguous photometric redshift is available.  The lens
redshifts entail rather big uncertainties, up to a few tens of
percent.  The lensing masses are uncertain at the same level.  On the
other hand, the lensing masses in the sample range from
$10^{11}M_\odot$ to $10^{13}M_\odot$; in comparison, the redshift
uncertainty is not so important in this preliminary analysis.
% \textcolor{red}{\bf IF: I would not say this is
% ``negligible'' but, rather, that the error in the redshift would lead to
%  surface mass density uncertainties of XX\%, which, for the
%  aim of the tentative analysis presented here, is an acceptable
%  result. You should also check and quantify properly the
%  uncertainty in the photo-z. What is the value claimed by the
%  CFHTLS group? I would say 5-10\% is a decent level, but you
%  are mentioning 10s of \% which is rather extreme!}.
% \textcolor{red}{\bf IF: Again, a simple quantification of the
% change you expect, for instance, if the source is at z=3 would be good.}
